Approximation as Differentiation

### 2025-05-24 main/introduction.tex
Tweaks questions in intro, placeholder for abstract.

Perera and collaborators introduced the idea of {\em Galois Program Slicing} as a particular conception of program slicing for provenance, described in several publications~\cite{perera12a,perera16d,ricciotti17}. Galois program slicing forms the basis of Perera's data visualisation tool \href{https://f.luid.org/}{Fluid} that allows interactive exploration of programmatically generated visualisations.

At a high level, Galois Program Slicing assumes that, for each possible value that may be input or output by a program, there exists a lattice of {\em approximations} of that value. For a particular run of a program that takes input $x$ and produces output $y$, we also get a Galois connection between the lattice of approximations of $x$ and the lattice of approximations of $y$. The right half of the Galois connection is the ``forward direction'' taking approximations of the input to approximations of the output; the left half of the Galois connection is the ``backward direction'' that takes approximations of the output to the least (i.e., most approximate) approximation of the input that gives rise to this output approximation.

>>>>

Perera and collaborators introduced the idea of {\em Galois Program Slicing} (hereafter, \GPS) as a particular conception of program slicing for provenance, described in several publications~\cite{perera12a,perera16d,ricciotti17}. \GPS forms the basis of Perera's data visualisation tool \href{https://f.luid.org/}{Fluid} that allows interactive exploration of programmatically generated visualisations.

At a high level, \GPS assumes that, for each possible value that may be input or output by a program, there exists a lattice of {\em approximations} of that value. For a particular run of a program that takes input $x$ and produces output $y$, we also get a Galois connection between the lattice of approximations of $x$ and the lattice of approximations of $y$. The right half of the Galois connection is the ``forward direction'' taking approximations of the input to approximations of the output; the left half of the Galois connection is the ``backward direction'' that takes approximations of the output to the least (i.e., most approximate) approximation of the input that gives rise to this output approximation.
